City traffic, IoT and Blockchain technologies

### 2020-10-22 thesis/report2.tex
Small advancements on report 2.

@@

@@

>>>>

    \paragraph{Security} The security is not a concern at this stage. The commmunications between the \textit{frontend} and the \textit{backend} have been described above only with respect to the form of communication. Any other aspects like encryption, certificates will be part of next sections.

    \paragraph{Anonimity} In the client server architecture 
    \citep{MicroservicesCityTrafficSimulation} the server does not need to maintain an identity of the clients which it has to communicate with. In order to keep an accurate list of how various lines and their load any client is required to send a report where it signals that it finished the traveling through a line. This can be seen in listing \ref{lst:jsonClientEnums}, first message type called \textit{ReportOffFromLine}. The momentarily assumption is that the clients are correctly behaving and are not actively trying to introduce unwanted effects into the wider network, nor to mislead the server about their position. Such enforcments, of mandatory good behavior, are modeled through mechanisms like Proof of Work and Proof of Stake and will be discussed in section \ref{sec:PoWandPoS}. The other aspect which can naturally occur is when a client, altough it has good intentions to send a \textit{ReportOffFromLine} message, it is not able to due to dropped connections or any other reason outside its control. A server might need, in this case, to implement a mechanism of timeouts for \textit{ReportOnTheLine}. In order to know which message to timeout it should keep an identification token for each client. This is one of the solutions. Knowing the average time to travel the respective line it can safely asssume that if there is no sign from that client within a reasonable and configurable time, it can dequeue its load.

    \paragraph{Interoperability} The plethora of programming languages, frameworks, runtimes and operating systems give a multitude of choices of where and how to run such clients and servers. So far nothing has been discussed regarding this aspect. The only place where we can see an implementation of a client server architecture, as presented in this section, is \cite{MicroservicesCityTrafficSimulation}. Programming language is Golang, the UI is made using web technologies like HTMl and JavaScript, together with various frameworks or libraries for ease of development (a library called Gorilla for working with WebSockets in Golang, OpenSourceMap and OpenLayers for displaying and manipulating maps in the browser, etc.). However, despite all those fine grained choices, the one which assures the interoperability is the ubiquity of JSON formats. Every language supports it and every language knows how to encode its internal data structures into a JSON format. Or how to decode them. Thus listings \ref{lst:jsonClientEnums} and \ref{lst:jsonEnvelope} are presented in as JSON messages schema. They also represents a small part of wannabe protocol.

@@

    \paragraph{Security} Security in Ethereum is a complex process. If an account, being a user's account or a contract account, has successfully secured the private signing key, it is assured that no one can simulate it and no one can execute transactions on its behalf. Known breaches have always occured in the same way: private keys have been leaked and malicious actors were able to execute transactions with them.
    An approach in securing IoT networks is described in \cite{SecureCommunicatingThingsNetworkFramework}. The aim is to ensure secure product shipment, as well as connecting manufacturing locations from different geographical locations. They have a front end for human interactions and a back end for the internal communication of the blockchain network. In the blockchain networks there are two types of associates, the authentication nodes also known is miners and execution nodes. The authentication nodes take care of validating new transactions and keeping up to date with the ever growing blockchain in which they participate. The executing nodes are watching accumulating values and verify their validity. The authors are considering various scenarios like traceability of product records, illegal activities made by workers or shippments. Transactions like those are always embedding the previous block's hash, providing a secure way around manipulating

@@

% good behavior
